Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2022-03-31 psy_peds_3.Rmd
correcting study dates

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- as.Date("2019-01-01")
history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-01-15")
end_date_plots <- as.Date("2021-05-01")
```

>>>>

```{r}
# cut-off dates used in the analysis, these should not be changed
# history_start_date <- as.Date("2019-01-01")
# history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-01-01")
end_date_plots <- as.Date("2021-06-01")
```
